\sysfull

### 2018-08-05 paper/asplos19/intro.tex
update intro fig

%
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/intro-figure-v3.pdf}
    \caption{\note{small static task subplot and large static task subplot can be re-arranged to fit next to each other, so we end up with two layers plot} Task coalescing at runtime reduces time and energy overhead in task-based intermittent programming models by performing fewer commits (denoted as \texttt{C}) of individual tasks (denoted as \texttt{Tx}). On the other hand, task splitting reduces wasted computation and enables termination for bigger tasks.}
    \label{fig:coalesce}
\end{figure}
%
%\textbf{Task Decomposition of Intermittent Programs.}

>>>>

%
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/intro-figure-horiz.pdf}
    \caption{Task coalescing at runtime reduces time and energy overhead in task-based intermittent programming models by performing fewer commits (denoted as \texttt{C}) of individual tasks (denoted as \texttt{Tx}). On the other hand, task splitting reduces wasted computation and enables termination for bigger tasks.}
    \label{fig:coalesce}
\end{figure}
%
%\textbf{Task Decomposition of Intermittent Programs.}
